---
title: "Website Behavior & Booking Funnel Analysis"
subtitle: "MEin3D | Google Analytics 4 | Jan 1 – Apr 21, 2026"
author: "Kathleen Juarez"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    embed-resources: true
    code-fold: true
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(scales)
library(knitr)
library(kableExtra)
```

## Data Loading

```{r}
#| label: load-data

# Sessions by channel (from Traffic Acquisition report)
sessions_raw <- read_csv("A05_data_sessions.csv", skip = 9, show_col_types = FALSE) |>
  rename(channel = 1, sessions = 2, total_users = 3) |>
  filter(!is.na(channel), channel != "")

# All events by channel (from Events report)
events_raw <- read_csv("A05_data_ga4-events.csv", skip = 9, show_col_types = FALSE) |>
  rename(event_name = 1, channel = 2, event_count = 3, total_users = 4) |>
  filter(!is.na(event_name), event_name != "")
```

## Data Preparation

```{r}
#| label: extract-events

# Helper: extract one event's Total users by channel
extract_event <- function(event_nm, col_name) {
  events_raw |>
    filter(event_name == event_nm) |>
    select(channel, {{ col_name }} := total_users)
}

# Funnel stages (using Total users, not event count)
page_view        <- extract_event("page_view",        page_views)
form_start       <- extract_event("form_start",       form_starts)
booking_complete <- extract_event("booking_complete", bookings)

# High-intent behavioral signals (context only — not sequential funnel gates,
# because form_start users exceed contact/appt users, indicating the form
# is accessible via multiple paths on the site)
schedule_appt <- extract_event("Schedule_Appointment", sched_appt_users)
contact_us    <- extract_event("contact_us",           contact_us_users)
```

```{r}
#| label: build-table

ga4_data <- sessions_raw |>
  select(channel, sessions) |>
  left_join(page_view,        by = "channel") |>
  left_join(form_start,       by = "channel") |>
  left_join(booking_complete, by = "channel") |>
  left_join(schedule_appt,    by = "channel") |>
  left_join(contact_us,       by = "channel") |>
  mutate(across(-channel, ~replace_na(., 0))) |>
  mutate(
    page_view_rate    = if_else(sessions > 0,    page_views  / sessions,   0),
    form_start_rate   = if_else(page_views > 0,  form_starts / page_views, 0),
    booking_rate      = if_else(form_starts > 0, bookings    / form_starts, 0),
    overall_conv_rate = if_else(sessions > 0,    bookings    / sessions,   0)
  )

totals <- ga4_data |>
  summarise(
    channel           = "TOTAL",
    sessions          = sum(sessions),
    page_views        = sum(page_views),
    form_starts       = sum(form_starts),
    bookings          = sum(bookings),
    sched_appt_users  = sum(sched_appt_users),
    contact_us_users  = sum(contact_us_users),
    overall_conv_rate = sum(bookings) / sum(sessions)
  )

site_avg <- totals$overall_conv_rate
```

## Statistical Summary

```{r}
#| label: summary-stats
#| echo: false

summary_df <- tibble(
  Metric = c(
    "Total Sessions",
    "Page View Users",
    "Form Start Users",
    "Bookings Completed",
    "Page View Rate (users)",
    "Form Start Rate (of page views)",
    "Booking Rate (of form starts)",
    "Overall Conversion Rate",
    "Largest Drop-off Stage"
  ),
  Value = c(
    comma(totals$sessions),
    comma(totals$page_views),
    comma(totals$form_starts),
    comma(totals$bookings),
    percent(totals$page_views  / totals$sessions,   accuracy = 0.1),
    percent(totals$form_starts / totals$page_views, accuracy = 0.1),
    percent(totals$bookings    / totals$form_starts, accuracy = 0.1),
    percent(site_avg,                               accuracy = 0.1),
    paste0("page_view → form_start (",
           percent(1 - totals$form_starts / totals$page_views, accuracy = 0.1),
           " drop-off)")
  )
)

summary_df |>
  kbl(align = c("l", "r"), col.names = c("Metric", "Value")) |>
  kable_styling(
    bootstrap_options = c("striped", "condensed", "bordered"),
    full_width = FALSE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#1A3A5C", color = "white") |>
  row_spec(9, bold = TRUE)
```
# Key Findings - The Core Problem

## Visual Evidence

### Funnel: Most Users Exit Before Starting the Booking Form

```{r}
#| label: fig-funnel
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Unique users at each stage of the booking funnel. Red bar indicates the largest drop-off point."

funnel_long <- tibble(
  stage = factor(
    c("Sessions", "Page Views", "Form Start", "Booking\nComplete"),
    levels = c("Sessions", "Page Views", "Form Start", "Booking\nComplete")
  ),
  count     = c(totals$sessions, totals$page_views, totals$form_starts, totals$bookings),
  highlight = c(FALSE, FALSE, TRUE, FALSE)
)

ggplot(funnel_long, aes(x = stage, y = count, fill = highlight)) +
  geom_col(width = 0.52) +
  geom_text(aes(label = comma(count)),
            vjust = -0.4, size = 3.8, fontface = "bold", color = "#1A1A1A") +
  scale_fill_manual(values = c("FALSE" = "#2E5F8A", "TRUE" = "#C0392B")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(title= "Most Users Exit Before Completing Any High-Intent Action", x = NULL, y = "Users") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "#EEEEEE"),
    axis.ticks         = element_blank(),
    legend.position    = "none"
  )
```

# Not all Traffic is created equal

### Conversion Rate by Traffic Channel

```{r}
#| label: fig-channels
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Booking conversion rate (booking_complete users ÷ sessions) by traffic channel. Dashed line indicates site average."

ga4_data |>
  mutate(
    channel   = fct_reorder(channel, overall_conv_rate),
    highlight = overall_conv_rate > site_avg
  ) |>
  ggplot(aes(x = channel, y = overall_conv_rate, fill = highlight)) +
  geom_col(width = 0.52) +
  geom_text(aes(label = percent(overall_conv_rate, accuracy = 0.1)),
            hjust = -0.15, size = 3.8, fontface = "bold", color = "#1A1A1A") +
  geom_hline(yintercept = site_avg, linetype = "dashed",
             color = "#888888", linewidth = 0.5) +
  annotate("text", x = 0.6, y = site_avg + 0.003,
           label = paste0("Site avg: ", percent(site_avg, accuracy = 0.1)),
           size = 3.2, color = "#888888", hjust = 0) +
  coord_flip() +
  scale_fill_manual(values = c("FALSE" = "#7FA8C9", "TRUE" = "#1D3D5C")) +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     expand = expansion(mult = c(0, 0.25))) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.x = element_line(color = "#EEEEEE"),
    axis.ticks         = element_blank(),
    legend.position    = "none"
  )
```

# Key Findings

## Booking Funnel Performance by Traffic Channel

```{r}
#| label: tbl-funnel
#| echo: false

ga4_data |>
  arrange(desc(overall_conv_rate)) |>
  bind_rows(totals) |>
  mutate(overall_conv_rate = percent(overall_conv_rate, accuracy = 0.1)) |>
  select(
    `Traffic Channel` = channel,
    `Sessions`        = sessions,
    `Page Views`      = page_views,
    `Contact Us`      = contact_us_users,
    `Form Starts`     = form_starts,
    `Sched. Appts`    = sched_appt_users,
    `Conv. Rate`      = overall_conv_rate
  ) |>
  kbl(align = c("l","c","c","c","c","c","c")) |>
  kable_styling(
    bootstrap_options = c("condensed", "bordered"),
    full_width = FALSE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#1B2A4A", color = "white") |>
  row_spec(seq(1, nrow(ga4_data), by = 2), background = "white",   color = "#333333") |>
  row_spec(seq(2, nrow(ga4_data), by = 2), background = "#EAF3FA", color = "#333333") |>
  row_spec(nrow(ga4_data) + 1, bold = TRUE, background = "#D6E8F5", color = "#1B2A4A") |>
  footnote(
    general = "Booking Funnel Performance by Traffic Channel (Jan 1–Apr 21, 2026). Channels sorted by descending conversion rate. Conv. Rate = booking_complete users ÷ sessions.",
    general_title = "",
    footnote_as_chunk = TRUE
  )
```

## Subgroup Validation: Drop-off by Channel

```{r}
#| label: tbl-dropoff
#| echo: false

ga4_data |>
  mutate(dropoff = 1 - form_start_rate) |>
  arrange(dropoff) |>
  select(
    `Traffic Channel` = channel,
    `Page Views`      = page_views,
    `Form Starts`     = form_starts,
    `Form Start Rate` = form_start_rate,
    `Drop-off Rate`   = dropoff
  ) |>
  mutate(across(c(`Form Start Rate`, `Drop-off Rate`),
                ~percent(., accuracy = 0.1))) |>
  kbl(align = c("l","c","c","c","c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "bordered"),
    full_width = FALSE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#1A3A5C", color = "white")
```

## High-Intent Behavioral Signals

> **Note:** `Schedule_Appointment` and `contact_us` are link clicks to the page hosting the booking form. They are reported here as behavioral context rather than sequential funnel stages, because `form_start` users exceed the combined click totals — indicating the form is reachable through multiple paths on the site.

```{r}
#| label: tbl-signals
#| echo: false

ga4_data |>
  arrange(desc(sessions)) |>
  bind_rows(totals) |>
  select(
    `Traffic Channel`    = channel,
    `Sessions`           = sessions,
    `Sched. Appt Clicks` = sched_appt_users,
    `Contact Us Clicks`  = contact_us_users,
    `Form Starts`        = form_starts,
    `Bookings`           = bookings
  ) |>
  kbl(align = c("l","c","c","c","c","c")) |>
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "bordered"),
    full_width = FALSE,
    font_size = 13
  ) |>
  row_spec(0, bold = TRUE, background = "#1A3A5C", color = "white") |>
  row_spec(nrow(ga4_data) + 1, bold = TRUE, background = "#D5E8F0")
```
