---
title: "From Clicks to Conversions"
subtitle: "AI Powered Email Personalization Strategies for MEin3D"
author: "Nerina Campos · Jessica Garcia · Kathleen Juarez · Krystal Lee · Serena Shi (Project Lead) | Faculty Lead: Dr. Elif Ozkaya"
format:
  revealjs:
    theme: default
    transition: slide
    slide-number: true
    footer: "MEin3D | IBM 6530 | Group 2"
    width: 1280
    height: 720
    css: mein3d-slides.css
    auto-scale: true
    smaller: true
    scrollable: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(tidyr)
```

---

## Business Problem & Project Overview

:::: {.columns}
::: {.column width="48%"}
::: red-box
**MEin3D** — small startup specializing in custom 3D-printed figurines for life's milestones.

MEin3D lacked **automated, personalized, data-driven communication** — limiting trust, engagement, and long-term customer value.
:::
:::
::: {.column width="52%"}

| AO | Question | Method |
|---|---|---|
| AO1 | Non-personalized baseline? | Funnel analysis |
| AO2 | Does AI affect trust? | One-way ANOVA |
| AO3 | Social behavior → engagement? | A/B test |
| AO4 | Which CTA drives lift? | Z-test |
| AO5 | Where do users drop off? | GA4 funnel |

:::
::::

---

## AO1 — Non-Personalized Baseline
*Jessica Garcia*

:::: {.columns}
::: {.column width="50%"}
```{r ao1-chart, fig.height=4}
tibble(
  stage = factor(c("Sent","Delivered","Opened","Clicked"),
                 levels=c("Sent","Delivered","Opened","Clicked")),
  n = c(77, 74, 20, 2)
) |>
ggplot(aes(x=stage, y=n)) +
  geom_bar(stat="identity", fill="#666", width=0.6) +
  geom_text(aes(label=n), vjust=-0.4, fontface="bold", size=6) +
  scale_y_continuous(limits=c(0,90)) +
  labs(title="Baseline Email Funnel — March 10", x=NULL, y="Recipients") +
  theme_minimal(base_size=14)
```
:::
::: {.column width="50%"}

| Metric | Value |
|---|---|
| Deliverability | **96.1%** |
| Open Rate | **27.3%** |
| Click-to-Open Rate | **10.0%** |
| Unsubscribes | **0** |

::: red-box
**Key finding:** 90% drop-off between open and click. The content and CTA are the bottleneck — not the subject line. This directly motivates AO4.
:::
:::
::::

---

## AO2 — AI Personalization & Trust
*Krystal Lee*

:::: {.columns}
::: {.column width="52%"}
```{r ao2-chart, fig.height=4.2}
tibble(condition=c("AI","Control"), mean_trust=c(4.24,4.16)) |>
ggplot(aes(x=condition, y=mean_trust, fill=condition)) +
  geom_bar(stat="identity", width=0.5) +
  geom_text(aes(label=mean_trust), vjust=-0.5, fontface="bold", size=7) +
  scale_fill_manual(values=c("AI"="#777","Control"="#aaa")) +
  scale_y_continuous(limits=c(0,5)) +
  labs(title="Average Trust Score by Condition",
       subtitle="10-item Likert scale (1–5) · n = 130",
       x=NULL, y="Score (1–5)") +
  theme_minimal(base_size=14) + theme(legend.position="none")
```
:::
::: {.column width="48%"}

| Statistic | Value |
|---|---|
| Mean Trust (AI) | **4.24** |
| Mean Trust (Control) | **4.16** |
| F-Statistic | **0.745** |
| p-Value | **0.39** |
| 95% CI (Tukey) | **[−0.280, 0.110]** |

::: red-box
AI personalization does **not** erode trust — **green light to scale personalized campaigns.**
:::
:::
::::

---

## AO3 — Social Behavior & Engagement
*Nerina Campos*

**Meta signals (likes, shares, saves, comments) used to classify subscribers → personalized vs. generic**

```{r ao3-table}
tibble(
  `Email Type`=c("Personalized","Generic"),
  `Subject Line`=c("Your Car Could Be Next 🚗","Something New Is Coming This April 🚗"),
  Sent=c(73,74), Opened=c(19,16), Clicked=c(4,0),
  `Open Rate`=c("26%","22%"), `Click Rate`=c("**5%**","**0%**")
) |>
kable(escape=FALSE) |>
  kable_styling(full_width=TRUE, font_size=20) |>
  row_spec(1, background="#fdecea", bold=TRUE)
```

::: red-box
**Personalization drives action** — 5% click rate vs. 0% for generic. Behavior-based messaging creates stronger connection and higher conversion potential.
:::

---

## AO4 — CTA Feature Optimization
*Serena Shi*

```{r ao4-chart, fig.height=3.6, fig.width=11}
tibble(
  metric=factor(rep(c("Open Rate (%)","CTR (%)","CTOR (%)"),each=2),
                levels=c("Open Rate (%)","CTR (%)","CTOR (%)")),
  condition=rep(c("Generic","Personalized"),3),
  value=c(23.1,29.9,1.38,3.56,5.6,11.4)
) |>
ggplot(aes(x=condition, y=value, fill=condition)) +
  geom_bar(stat="identity", width=0.55) +
  geom_text(aes(label=paste0(value,"%")), vjust=-0.4, fontface="bold", size=5.5) +
  scale_fill_manual(values=c("Generic"="#888","Personalized"="#c0392b")) +
  facet_wrap(~metric, scales="free_y") +
  labs(title="Personalized CTA vs. Generic — 5 Campaign Rounds", x=NULL, y=NULL) +
  theme_minimal(base_size=14) +
  theme(legend.position="bottom", strip.text=element_text(face="bold",size=13))
```

:::: {.columns}
::: {.column width="33%"}
::: stat-box-dark
Open Rate **+6.7pp**\
23.1% → 29.9%
:::
:::
::: {.column width="33%"}
::: stat-box-dark
CTR **+2.6×**\
1.38% → 3.56%
:::
:::
::: {.column width="33%"}
::: hero-metric
CTOR **+2×**\
5.6% → 11.4%\
Z = −1.90, p = 0.058
:::
:::
::::

---

## AO5 — Website Funnel Analysis
*Kathleen Juarez*

:::: {.columns}
::: {.column width="50%"}
```{r ao5-funnel, fig.height=4.2}
tibble(
  stage=factor(c("Sessions","Page Views","Form Start","Bookings"),
               levels=c("Sessions","Page Views","Form Start","Bookings")),
  n=c(563,470,38,5),
  fill=c("a","a","b","c")
) |>
ggplot(aes(x=stage, y=n, fill=fill)) +
  geom_bar(stat="identity", width=0.6) +
  geom_text(aes(label=n), vjust=-0.4, fontface="bold", size=7) +
  scale_fill_manual(values=c("a"="#1a3a5c","b"="#c0392b","c"="#27ae60")) +
  scale_y_continuous(limits=c(0,640)) +
  labs(title="Booking Funnel — Jan 1 to Apr 21, 2026", x=NULL, y="Users") +
  theme_minimal(base_size=14) + theme(legend.position="none")
```
:::
::: {.column width="50%"}

| Channel | Sessions | Conv. Rate |
|---|---|---|
| Unassigned | 32 | **3.1%** |
| Organic Search | 86 | **2.3%** |
| Organic Social | 207 | 0.5% |
| Direct | 213 | 0.5% |
| **TOTAL** | **563** | **0.9%** |

::: red-box
**99.1% of visitors leave without booking.** Sharpest drop at Form Start. Organic Search converts 4× better than Social.
:::
:::
::::

---

## Recommendations & Summary

:::: {.columns}
::: {.column width="50%"}
**Immediate (0–30 days)**

::: rec-item
Deploy AI-personalized CTAs — 2.6× CTR, trust preserved
:::
::: rec-item
Fix the booking form — 92% drop-off at Form Start
:::

**Medium-Term (30–90 days)**

::: rec-item
Invest in Organic Search — highest converting channel
:::
::: rec-item
Scale A/B testing to n ≈ 600+ to confirm AO4
:::

**Long-Term (90+ days)**

::: rec-item
Build automated email nurture sequences
:::
::: rec-item
Implement GA4 purchase event tracking
:::
:::
::: {.column width="50%"}

| AO | Key Finding |
|---|---|
| AO1 | 10% CTOR baseline — content is bottleneck |
| AO2 | AI preserves trust (p = 0.39) |
| AO3 | 5% click vs. 0% generic |
| AO4 | **2× CTOR, 2.6× CTR** lift |
| AO5 | 99.1% don't book — fix funnel |

::: big-quote
The trust is there. The lift is real. Fix the funnel.
:::
:::
::::

---

## Thank You

::: thank-you-box
**Group 2 — IBM 6530**

Nerina Campos · Jessica Garcia · Kathleen Juarez · Krystal Lee · **Serena Shi (Project Lead)**

*Faculty Lead: Dr. Elif Ozkaya*

GitHub: [github.com/soserena/mein3d_project](https://github.com/soserena/mein3d_project)
:::