---
title: "MEin3D"
subtitle: "Deliverable 1 — Final Dashboard"
format: 
  dashboard:
    orientation: columns
    theme: minty
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(scales)
library(ggplot2)
library(dplyr)
library(DBI)
library(bigrquery)
```

```{r}
#| label: bq-connect
#| include: false

project_id <- "mein3d-487204"

bigrquery::bq_auth()

con <- dbConnect(
  bigrquery::bigquery(),
  project = project_id,
  billing = project_id
)

con  # verify connection
```

```{r}
#| label: bq-query
#| include: false

sql <- "
  WITH base AS (
    SELECT
      event_name,
      user_pseudo_id,
      CASE
        WHEN traffic_source.medium = 'organic'               THEN 'Organic Search'
        WHEN traffic_source.medium = 'referral'              THEN 'Referral'
        WHEN traffic_source.medium = 'cpc'                   THEN 'Paid Search'
        WHEN LOWER(traffic_source.source) LIKE '%instagram%'
          OR LOWER(traffic_source.source) LIKE '%facebook%'
          OR LOWER(traffic_source.source) LIKE '%tiktok%'    THEN 'Organic Social'
        WHEN traffic_source.medium IS NULL
          OR traffic_source.medium = '(none)'                THEN 'Direct'
        ELSE 'Unassigned'
      END AS channel
    FROM `mein3d-487204.analytics_513869218.events_*`
    WHERE _TABLE_SUFFIX BETWEEN '20260101' AND '20260421'
  ),
  sessions AS (
    SELECT
      channel,
      COUNT(DISTINCT user_pseudo_id) AS sessions
    FROM base
    WHERE event_name = 'session_start'
    GROUP BY channel
  ),
  event_users AS (
    SELECT
      channel,
      event_name,
      COUNT(DISTINCT user_pseudo_id) AS total_users
    FROM base
    WHERE event_name IN (
      'page_view',
      'form_start',
      'booking_complete',
      'Schedule_Appointment',
      'contact_us'
    )
    GROUP BY channel, event_name
  )
SELECT
  s.channel,
  s.sessions,
  MAX(CASE WHEN e.event_name = 'page_view'            THEN e.total_users ELSE 0 END) AS page_views,
  MAX(CASE WHEN e.event_name = 'form_start'           THEN e.total_users ELSE 0 END) AS form_starts,
  MAX(CASE WHEN e.event_name = 'booking_complete'     THEN e.total_users ELSE 0 END) AS bookings,
  MAX(CASE WHEN e.event_name = 'Schedule_Appointment' THEN e.total_users ELSE 0 END) AS sched_appt_users,
  MAX(CASE WHEN e.event_name = 'contact_us'           THEN e.total_users ELSE 0 END) AS contact_us_users
FROM sessions s
LEFT JOIN event_users e ON s.channel = e.channel
GROUP BY s.channel, s.sessions
ORDER BY s.sessions DESC
"
ga4_data <- dbGetQuery(con, sql)
```

```{r}
#| label: prepare-data-a05
#| include: false

ga4_data <- ga4_data |>
  mutate(across(-channel, ~replace_na(., 0))) |>
  mutate(
    page_view_rate    = if_else(sessions > 0,    page_views  / sessions,   0),
    form_start_rate   = if_else(page_views > 0,  form_starts / page_views, 0),
    booking_rate      = if_else(form_starts > 0, bookings    / form_starts, 0),
    overall_conv_rate = if_else(sessions > 0,    bookings    / sessions,   0)
  )

totals <- ga4_data |>
  summarise(
    channel           = "TOTAL",
    sessions          = sum(sessions),
    page_views        = sum(page_views),
    form_starts       = sum(form_starts),
    bookings          = sum(bookings),
    sched_appt_users  = sum(sched_appt_users),
    contact_us_users  = sum(contact_us_users),
    overall_conv_rate = sum(bookings) / sum(sessions)
  )

site_avg <- totals$overall_conv_rate

dbDisconnect(con)
```

# AO1 – AO3 {orientation="columns"}

## left-col {width="50%"}

::: {.card title="AO1 – Placeholder"}
**[PLACEHOLDER — AO1 Team Member]**

Add your visualization or analysis here.

*Instructions:*

1. Load your data in a setup chunk at the top of the file.
2. Replace this card's contents with your `ggplot()` or table code.
3. Update the card title to reflect your chart or key finding.
:::

::: {.card title="AO2 – Placeholder"}
**[PLACEHOLDER — AO2 Team Member]**

Add your visualization or analysis here.
:::

## right-col {width="50%"}

::: {.card title="AO3 – Placeholder"}
**[PLACEHOLDER — AO3 Team Member]**

Add your visualization or analysis here.
:::

# AO4 – AO5 {orientation="columns"}

## left-col {width="50%"}

::: {.card title="AO4 – Placeholder"}
**[PLACEHOLDER — AO4 Team Member]**

Add your visualization or analysis here.
:::

::: {.card title="Booking Conversion Rate by Traffic Channel"}
```{r}
#| label: fig-channels
#| fig-width: 10
#| fig-height: 6
#| out-width: "100%"
#| out-height: "100%"

ga4_data |>
  mutate(
    channel   = fct_reorder(channel, overall_conv_rate),
    highlight = overall_conv_rate > site_avg
  ) |>
  ggplot(aes(x = channel, y = overall_conv_rate, fill = highlight)) +
  geom_col(width = 0.52) +
  geom_text(aes(label = percent(overall_conv_rate, accuracy = 0.1)),
            hjust = -0.15, size = 3.8, fontface = "bold", color = "#1A1A1A") +
  geom_hline(yintercept = site_avg, linetype = "dashed",
             color = "#888888", linewidth = 0.5) +
  annotate("text", x = 0.6, y = site_avg + 0.003,
           label = paste0("Site avg: ", percent(site_avg, accuracy = 0.1)),
           size = 3.2, color = "#888888", hjust = 0) +
  coord_flip() +
  scale_fill_manual(values = c("FALSE" = "#7FA8C9", "TRUE" = "#1D3D5C")) +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     expand = expansion(mult = c(0, 0.25))) +
  labs(
    title    = "Not All Traffic Is Created Equal",
    subtitle = "Conv. rate = booking_complete users ÷ sessions | Dashed = site avg",
    x        = NULL,
    y        = NULL
  ) +
  theme_minimal(base_size = 18) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.x = element_line(color = "#EEEEEE"),
    axis.ticks         = element_blank(),
    legend.position    = "none"
  )
```
:::

## right-col {width="50%"}

::: {.card title="Booking Funnel: Most Users Exit Before the Form"}
```{r}
#| label: fig-funnel
#| fig-width: 10
#| fig-height: 6
#| out-width: "100%"
#| out-height: "100%"

funnel_long <- tibble(
  stage = factor(
    c("Sessions", "Page Views", "Form Start", "Booking\nComplete"),
    levels = c("Sessions", "Page Views", "Form Start", "Booking\nComplete")
  ),
  count     = c(totals$sessions, totals$page_views, totals$form_starts, totals$bookings),
  highlight = c(FALSE, FALSE, TRUE, FALSE)
)

ggplot(funnel_long, aes(x = stage, y = count, fill = highlight)) +
  geom_col(width = 0.52) +
  geom_text(aes(label = comma(count)),
            vjust = -0.4, size = 3.8, fontface = "bold", color = "#1A1A1A") +
  scale_fill_manual(values = c("FALSE" = "#2E5F8A", "TRUE" = "#C0392B")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    title    = "Most Users Exit Before Completing Any High-Intent Action",
    subtitle = "Red bar = largest drop-off point (page view → form start)",
    x        = NULL,
    y        = "Users"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "#EEEEEE"),
    axis.ticks         = element_blank(),
    legend.position    = "none"
  )
```
:::